---
title: "Assignment Table WebScraping"
format: html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = TRUE, 
                      fig.align  = "center",
                      fig.height = 3, fig.width = 4)
ggplot2::theme_set(ggplot2::theme_bw() + ggplot2::theme(strip.background = ggplot2::element_rect(fill = "white")))
```

```{r}
  if (!require("pacman")) install.packages("pacman")

# Load contributed packages with pacman
pacman::p_load(rvest, dplyr, tidyverse, xml2)
```

# Problem:

Go to the following page [List of U.S. states and territories by population](https://en.wikipedia.org/wiki/List_of_U.S._states_and_territories_by_population) and select the table `State and territory rankings`.
Your assignment is clear, well‑structured, and absolutely appropriate for an introductory web‑scraping task in R. It checks all the essential boxes: selecting the right table, cleaning column names, fixing data types, and handling missing values. If anything, I’d say it’s a solid foundation — the kind of exercise that teaches practical, real‑world scraping skills without overwhelming you.

That said, you can make it slightly more precise and a bit more “data‑science‑ready.” Here’s how I’d refine it:


1.  Import the table into R  

    - Use `rvest` to scrape the table.  
  
    - Ensure you select the correct table (the page contains multiple tables).


2.  Clean and standardize the data  

    - Fix column names so they are syntactically valid and descriptive (e.g., using `janitor::clean_names()`).
  
    - Ensure the first row is treated as column headers, not data.
  
  

3.  Correct column classes 


    - Convert numeric columns to numeric (they often import as character because of commas or symbols).  

    - Convert rank columns to integers.  

    - Convert state/territory names to character.
  


4.  Handle missing values  


     - Replace any `"—"` or `"__"` or similar placeholders with `NA`.
  


5. (Optional but useful)  


    - Remove commas from numbers.  

    - Check for duplicated rows.  

    - Verify that the number of rows matches the number of U.S. states + territories.
